### 2023-02-04 alignpair_letter.tex
Add testing github repo
Additional comments and changes by Reed

% title goes here:
\begin{flushleft}
{\Large\textbf{COATi: statistical pairwise alignment of protein coding sequences}}
\newline
% authors go here:
\\
Juan J. Garcia Mesa\textsuperscript{1,2},
Ziqi Zhu\textsuperscript{1,3},
Reed A. Cartwright\textsuperscript{1,3}
\\
\bigskip
1 Biodesign Institute, Arizona State University
\\
2 Ira A. Schools of Engineering, Arizona State University
\\
3 School of Life Sciences, Arizona State University
\\
\bigskip
* corresponding@author.mail

@@

\section*{Availability}
The source code for COATi, along with documentation, is
freely available on GitHub: \url{https://github.com/CartwrightLab/coati} and is
implemented in C++.
Code to replicate the analysis can be found on GitHug: \url{https://github.com/jgarciamesa/TODO}.

@@

@@

\subsection*{Funding}
This research was funded by an NSF-IIBR grant (\green{grant number}).\\

@@

>>>>

% title goes here:
\begin{flushleft}
{\Large\textbf{COATi: statistical pairwise alignment of protein coding sequences}}
\newline
% authors go here:
\\
Juan J. Garcia Mesa\textsuperscript{1,2},
Ziqi Zhu\textsuperscript{1,3},
Reed A. Cartwright\textsuperscript{1,3,*}
\\
\bigskip
1 Biodesign Institute, Arizona State University
\\
2 Ira A. Schools of Engineering, Arizona State University
\\
3 School of Life Sciences, Arizona State University
\\
\bigskip
* cartwright@asu.edu

@@

\section*{Availability}
The source code for COATi, along with documentation, is
freely available on GitHub: \url{https://github.com/CartwrightLab/coati} and is
implemented in C++.
Code to replicate the analysis can be found on GitHug: \url{https://github.com/jgarciamesa/coati-testing}.

@@

\TODO{This}

@@

\subsection*{Funding}
This research was funded by NSF award DBI-1929850.\\

@@

\TODO{Juan, check all references for consistency.}
